### 2022-06-06 src/ms.tex
minor

\subsection{The curse of dimensionality and the no-free-lunch theorem}
The \emph{curse of dimensionality} refers to a phenomenon where the
\emph{volume} of \emph{possible} explanations for the data grows exponentially
with increasing dimension of the problem. Consider the following
example\footnote{ Taken from the excellent paper by \citet{arXiv:2104.00008}.
}. There are images consisting of $n$ pixels where each of the pixels is either
a black (0) or white (1). The number of possible images is $2^n$ which grows
exponentially. If each image out of the $2^n$ possible images is described by
one of two labels $A$, or $B$ then the total number of possible ways of
labeling the set of images is $2^{2^n}$ which is a stupidly large number. If
$n=9$, the number of ways to classify the set of all 9-bit black and white
images is greater than the number of atoms in the observable universe. If the
labels don't correlate with the properties of the images then one strategy for
solving this problem would be the lookup table approach -- memorize each image
with its label. The famous \emph{no-free-lunch} (NFLT) theorem proved by the
mathematician David Wolpert \citep{wolpert1996} demonstrates that it is
impossible to construct an algorithm which does better than the lookup table
approach.

@@

\subsubsection{MLE for a Gaussian linear model}
\subsection{The Laplace approximation}
\subsection{Gaussian linear models}

%\subsection{Machine learning and the difference between inference and prediction}
%% mention that even if we have a model focused on inference, it might be best if we judge 
%% its quality through its predictive performance
%
\subsection{Sampling and optimization methods}
%\subsubsection{The Laplace approximation}
%\subsubsection{Variational inference}
%\subsubsection{Importance sampling}
%\subsubsection{Rejection sampling}
%\subsubsection{Markov Chain Monte Carlo}
%\subsubsection{Hamiltonian Monte Carlo}
%\subsubsection{Other notable methods}
%
%\subsection{Model validation and comparison}
%\label{ssec:model_comparisonGaussian linear }
%
``Furthermore, in the future, a blind search for planetary signals will not
turn up all potential competing models unless those models
are specifically considered.''\citep{2017AJ....153..129J}.
\citet{2021AJ....162...59R}
\citet{2020AJ....160...17H}

>>>>

\subsection{The curse of dimensionality and the no-free-lunch theorem}
The \emph{curse of dimensionality} refers to a phenomenon where the
\emph{volume} of \emph{possible} explanations for the data grows exponentially
with increasing dimension of the problem. Consider the following
example\footnote{ Taken from the excellent paper by \citet{arXiv:2104.00008}.
}. There are images consisting of $n$ pixels where each of the pixels is either
a black (0) or white (1). The number of possible images is $2^n$ which grows
exponentially. If each image out of the $2^n$ possible images is described by
one of two labels $A$, or $B$ then the total number of possible ways of
labeling the set of images is $2^{2^n}$ which is a stupidly large number. If
$n=9$, the number of ways to classify the set of all 9-bit black and white
images is greater than the number of atoms in the observable universe. If the
labels don't correlate with the properties of the images then one strategy for
solving this problem would be the lookup table approach -- memorize each image
with its label. The famous \emph{no-free-lunch theorem} (NFLT) proved by the
mathematician David Wolpert \citep{wolpert1996} demonstrates that it is
impossible to construct an algorithm which does better than the lookup table
approach.

@@

\subsubsection{MLE for a Gaussian linear model}

\subsection{Gaussian linear models}

%\subsection{Machine learning and the difference between inference and prediction}
%% mention that even if we have a model focused on inference, it might be best if we judge 
%% its quality through its predictive performance
%
\subsection{Sampling and optimization methods}
\subsubsection{The Laplace approximation}
\subsubsection{Variational inference}
\subsubsection{Importance sampling}
\subsubsection{Rejection sampling}
\subsubsection{Markov Chain Monte Carlo}
\subsubsection{Hamiltonian Monte Carlo}
%\subsubsection{Other }
%
%\subsection{Model validation and comparison}
%\label{ssec:model_comparisonGaussian linear }
%
``Furthermore, in the future, a blind search for planetary signals will not
turn up all potential competing models unless those models
are specifically considered.''\citep{2017AJ....153..129J}.
\citet{2021AJ....162...59R}
\citet{2020AJ....160...17H}
